Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-06-18 manuscript_results.Rmd
code review line 1643

# Plot
plot(subset_data$target_end_date, subset_data$cases, type = "l",
     xlab = "Date", ylab = "Cases", main = "Cases - Last 2 Years")
```

@@

@@

Mean difference and standard deviation

# Define significance threshold  
alpha <- 0.05

>>>>

# Plot
plot(subset_data$target_end_date, subset_data$cases, type = "l",
     xlab = "Date", ylab = "Cases", main = "Cases - Last 2 Years")
```
Plotting conceptual image

@@

Here we are plotting the mean differences and standard deviation

```{r}
# Define significance threshold  
alpha <- 0.05

@@
